---
title: "R19 Coy Analysis"
author: "Patrick Snelgar"
date: "`r {format(Sys.Date(), '%d %B %Y')}`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(coyparser)
library(magrittr)


# 3% hicane, 1% BU, 2% BU, 4% BU, 6% BU,  2% AB, 4% Lonza, Control 
treatment_colours <- c("HiCane 3%" = "tomato", 
					   "Budup 1%" = "dodgerblue", 
					   "Budup 2%" = "mediumseagreen", 
					   "Budup 4%" = "plum", 
					   "Budup 6%" = "orange2", 
					   "AB 2%" = "mediumturquoise", 
					   "Budup Lonza 4%" = "lightsalmon4",  
					   "Untreated control" = "gray27")

```


```{r, funcitons, include=FALSE}

getBudDistribution <- function(c) {
	tmp <- NULL
	
	buds <- gsub("L([0-9]*)", "", c$coy, ignore.case = TRUE) %>%
				gsub("[,]", "", .)
	
	for (i in 1:length(buds)) {
		flowerChars <- strsplit(buds[i], "")[[1]]
		t <- c$Treatment[i]
		
		if(!is.null(tmp))
			tmp %<>% bind_rows(data.frame(flowers = flowerChars, treatment = t, stringsAsFactors = FALSE))
		else
			tmp <- data.frame(flowers = flowerChars, treatment = t, stringsAsFactors = FALSE)
	}
	
	return(table(tmp) %>% data.frame())

}

```

Script requires 'coyparser' package, install it as follows:

Generate a Github PAT (Public Access Token): https://help.github.com/en/github/authenticating-to-github/creating-a-personal-access-token-for-the-command-line#creating-a-token

set the token in the R environment, this will not be a persistent variable but is only needed when installing the library.
copy/paste this code into the terminal: Sys.setenv(GITHUB_PAT="ba05dd1...d5a87f9")

then use the devtools library to install the library: devtools::install_github("patricksnelgar/coyparser")
if you dont have devtools it can be installed with: install.packages("devtools")


```{r data_import, include=FALSE}


coy <- read_csv("./data/R19 Coy 2019 & treatments.csv") %>%
			mutate(coy = convertLegacyFormat(coy)) %>%
			filter(batchValidateCoy(coy)) %>%
			rename("CaneID" = 1) %>%
			select(CaneID, coy, Treatment)

caneInfo <- read_csv("./data/Red fox cane lengths.csv") %>%
				rename(CaneID = `Cane ID`) %>%
				filter(CaneID %in% coy$CaneID) %>%
				arrange(CaneID)

```
```{r floral_analysis, echo=FALSE}
	
output <- NULL

for (i in 1:length(coy$Treatment)) {
	f <- extractFloralShoots(coy$coy[i])
	flist <- splitChars(f)[[1]]
	t <- coy$Treatment[i]
	if(!is.null(output))
		output %<>% bind_rows(data.frame(flowers = flist, treatment = t, stringsAsFactors = FALSE))
	else
		output <- data.frame(flowers = flist, treatment = t, stringsAsFactors = FALSE)
	
}

flowerDist <- table(output) %>%
				data.frame() %>%
				filter(flowers != "l") %>%
				mutate(treatment = gsub("[ ][ ]+", " ", treatment), timing = str_extract(treatment, "[LMEV]+$"), timing = replace(timing, is.na(timing), "C")) %>%
				mutate(treatment = factor(treatment, levels = c("HiCane 3% + 0.2% Driftstop E", "HiCane 3% M", "HiCane 3% L", "HiCane 3% VL", "Untreated control",
							  "Budup 1% + AB 2% E", "Budup 1% + AB 2% M", "Budup 1% + AB 2% L", "Budup 1% + AB 2% VL", "AB 2% M",
							  "Budup 2% + AB 2% E", "Budup 2% + AB 2% M", "Budup 2% + AB 2% L", "Budup 2% + AB 2% VL", "Budup Lonza 4% + AB 2% M",
							  "Budup 4% + AB 2% E" , "Budup 4% + AB 2% M", "Budup 4% + AB 2% L", "Budup 4% + AB 2% VL", "", 
							  "Budup 6% + AB 2% E", "Budup 6% + AB 2% M", "Budup 6% + AB 2% L", "Budup 6% + AB 2% VL", " "))) %>%
				group_by(treatment) %>%
				mutate(percKF = Freq / sum(Freq))


f <- flowerDist %>%
	ggplot(aes(flowers, percKF, fill = timing)) +
		geom_bar(stat = "identity") +
		facet_wrap(~treatment, ncol = 5, scales = "free", drop = FALSE) +
		coord_cartesian(ylim = c(0, 0.5)) + 
		theme_bw() +
		ggtitle("Distribution of KFs per floral shoot") +
		labs(y = "Flower Distribution (%)", x = "King Flowers per shoot", fill = "Application Timing") + 
		theme_bw() +
		theme(legend.position = "bottom")  

```


```{r all_buds_analysis, echo=FALSE}



coyDist <- getBudDistribution(coy) %>%
			mutate(treatment = gsub("[ ][ ]+", " ", treatment), timing = str_extract(treatment, "[LMEV]+$"),
				   chemical = gsub("^([A-Za-z ]+[ ][0-9]%)(.+)", "\\1", treatment)) %>%
			mutate(treatment = factor(treatment, levels = c("HiCane 3% + 0.2% DS E", "HiCane 3% + 0.2% DS M", "HiCane 3% + 0.2% DS L", 
							  "HiCane 3% + 0.2% DS VL", "Untreated control", "Budup 1% + AB 2% E", "Budup 1% + AB 2% M",
							  "Budup 1% + AB 2% L", "Budup 1% + AB 2% VL", "AB 2% M", "Budup 2% + AB 2% E", "Budup 2% + AB 2% M", 
							  "Budup 2% + AB 2% L", "Budup 2% + AB 2% VL", "Budup Lonza 4% + AB 2% M", "Budup 4% + AB 2% E" , 
							  "Budup 4% + AB 2% M", "Budup 4% + AB 2% L", "Budup 4% + AB 2% VL", "",  "Budup 6% + AB 2% E", 
							  "Budup 6% + AB 2% M", "Budup 6% + AB 2% L", "Budup 6% + AB 2% VL", " "))) %>%
			group_by(treatment) %>%
			mutate(percKF = Freq / sum(Freq))
			

coyInfo <- data.frame(ID = coy$CaneID, treatment = coy$Treatment, BB = budBreak(coy$coy) * 100, 
					  KF = kingFlowers(coy$coy), WB = winterBuds(coy$coy), 
					  laterals = lateralFlowers(coy$coy),
					  caneLength = caneInfo$Length) %>%
			mutate(treatment = gsub("[ ][ ]+", " ", treatment)) %>%
			mutate(treatment = factor(treatment, levels = c("HiCane 3% + 0.2% DS E", "HiCane 3% + 0.2% DS M", "HiCane 3% + 0.2% DS L", 
							  "HiCane 3% + 0.2% DS VL", "Untreated control", "Budup 1% + AB 2% E", "Budup 1% + AB 2% M",
							  "Budup 1% + AB 2% L", "Budup 1% + AB 2% VL", "AB 2% M", "Budup 2% + AB 2% E", "Budup 2% + AB 2% M", 
							  "Budup 2% + AB 2% L", "Budup 2% + AB 2% VL", "Budup Lonza 4% + AB 2% M", "Budup 4% + AB 2% E" , 
							  "Budup 4% + AB 2% M", "Budup 4% + AB 2% L", "Budup 4% + AB 2% VL", "",  "Budup 6% + AB 2% E", 
							  "Budup 6% + AB 2% M", "Budup 6% + AB 2% L", "Budup 6% + AB 2% VL", " ")))

coyInfo %<>% 
	group_by(treatment) %>% 
	summarise(BudBreak = paste(format(mean(BB), digits = 3), "%", sep = ""), 
			  KFperWB = format(mean(KF/WB), digits = 3),
			  LperWB = format(mean(laterals/WB), digits = 3),
			  KFperM = format(mean(KF/(caneLength/250)), digits = 2))

coyDist %>%
	ggplot(aes(flowers, percKF, fill = timing)) +
		geom_bar(stat = "identity") +
		facet_wrap(~treatment, ncol = 5, scales = "free", drop = FALSE) +
		ylim(0, 0.5) + 
		labs(y = "Flower Distribution (%)", x = "King Flowers per shoot", main = "COY distribution for R19", fill = "Application Timing") + 
		theme_bw() +
		theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5, size = 20)) + 
		scale_fill_discrete(labels = c("Early", "Mid", "Late", "Very late", "Control")) +
		geom_text(data = coyInfo, aes(8, 0.48, label = paste( "BB:", BudBreak)), hjust = "left", inherit.aes = FALSE) + 
		geom_text(data = coyInfo, aes(8, 0.40, label = paste("LperWB:", LperWB)), hjust = "left", inherit.aes = FALSE) +
		geom_text(data = coyInfo, aes(8, 0.32, label = paste("KF per m2:", KFperM)), hjust = "left", inherit.aes = FALSE) + 
		ggtitle("R19 - Distribution of KF per shoot")

ggsave("./Graphs/R19 - Distribution of shoot type.png", width = 20, height = 12)


```


```{r report_graph, echo = FALSE}

coyDist <- table(tmp) %>%
			data.frame() %>%
			mutate(treatment = gsub("[ ][ ]+", " ", treatment), timing = str_extract(treatment, "[LMEV]+$"),
				   chemical = gsub("^([A-Za-z ]+[ ][0-9]%)(.+)", "\\1", treatment)) %>%
			mutate(treatment = factor(treatment, 
									  levels = c("HiCane 3% + 0.2% DS E", "HiCane 3% + 0.2% DS M", "HiCane 3% + 0.2% DS L", "HiCane 3% + 0.2% DS VL", 
									  		   "Budup 1% + AB 2% E", "Budup 1% + AB 2% M", "Budup 1% + AB 2% L", "Budup 1% + AB 2% VL", 
									  		   "Budup 2% + AB 2% E", "Budup 2% + AB 2% M", "Budup 2% + AB 2% L", "Budup 2% + AB 2% VL", 
									  		   "Budup 4% + AB 2% E", "Budup 4% + AB 2% M", "Budup 4% + AB 2% L", "Budup 4% + AB 2% VL", 
									  		   "Budup 6% + AB 2% E", "Budup 6% + AB 2% M", "Budup 6% + AB 2% L", "Budup 6% + AB 2% VL", 
									  		   "Untreated control", "AB 2% M", "Budup Lonza 4% + AB 2% M"))) %>%
			group_by(treatment) %>%
			mutate(percKF = Freq / sum(Freq))



coyDist %>%
	ggplot(aes(flowers, percKF, fill = chemical)) +
		geom_bar(stat = "identity") +
		facet_wrap(~treatment, ncol = 4, scales = "free", drop = TRUE) +
		ylim(0, 0.5) + 
		labs(y = "Flower Distribution (%)", x = "King Flowers per shoot", main = "COY distribution for R19", fill = "Chemical") + 
		theme_bw() +
		theme(legend.position = "bottom", 
			  legend.background = element_rect(colour = "black", linetype = 1),
			  plot.title = element_text(hjust = 0.5, size = 24), 
			  strip.text.x = element_text(size = 12)) + 
		scale_fill_manual(values = treatment_colours) +
		#geom_text(data = coyInfo, aes(8, 0.48, label = paste( "BB:", BudBreak)), hjust = "left", inherit.aes = FALSE) + 
		#geom_text(data = coyInfo, aes(8, 0.40, label = paste("LperWB:", LperWB)), hjust = "left", inherit.aes = FALSE) +
		geom_text(data = coyInfo, aes(8.7, 0.35, label = paste("KF per m² :", KFperM)), hjust = "left", inherit.aes = FALSE) 
		#ggtitle("R19 - Distribution of King Flowers per shoot")

ggsave("./Graphs/R19 - Distribution of KF pershoot by chemical (colour corrected).png", width = 20, height = 12)

```

Minimalistic flower distributon by shoot graph for steering group April 2021

```{r}

coyDist <- 
	getBudDistribution(coy) %>%
	mutate(treatment = gsub("[ ][ ]+", " ", treatment), timing = str_extract(treatment, "[LMEV]+$"),
				   chemical = gsub("^([A-Za-z ]+[ ][0-9]%)(.+)", "\\1", treatment)) %>%
	filter(treatment %in% c("HiCane 3% + 0.2% DS E", "HiCane 3% + 0.2% DS L", "Untreated control")) %>%
	mutate(treatment = factor(treatment, levels = c("HiCane 3% + 0.2% DS E", "HiCane 3% + 0.2% DS L", "Untreated control"))) %>%
	group_by(treatment) %>%
	mutate(percKF = Freq / sum(Freq))

coyDist %>%
	ggplot(aes(flowers, percKF, fill = chemical)) +
		geom_bar(stat = "identity") +
		facet_wrap(~treatment) +
		ylim(0, 0.5) + 
		labs(y = "Flower Distribution (%)", x = "King Flowers per shoot", main = "COY distribution for R19", fill = "Chemical") + 
		theme_bw() +
		theme(legend.position = "bottom", 
			  legend.background = element_rect(colour = "black", linetype = 1),
			  plot.title = element_text(hjust = 0.5, size = 24), 
			  strip.text.x = element_text(size = 12)) + 
		scale_fill_manual(values = treatment_colours)

ggsave("./Graphs/R19 - Distribution of KF pershoot by chemical (HC & Control).png", width = 12, height = 6)

```